---
title: "Original Homework Code"
author: "Christopher A Schmitt"
date: "September 16, 2019"
output: html_document
---

***

#Introduction to the Assignment

***

This is the code for [Homework 02](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week three of AN597. THis is homework associated with Modules 6 and 7.

The first question asks:

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

##Question 1

Question 1: What is the probability that she will hear more than 8 calls during any given session?

If her previous belief is that she will hear 15 calls in a 2 hours timeframe (let's call that the average), then the probability of hearing 8 in that 2 hour timeframe, given a Poisson distribution, should be given by the equation:
```{r}
#here's my code
x<-5*8
x
```
 OK, that answer makes sense I guess.
 
##Question 2

 Next question:
```{r}
#New chunk
```
 
#CHALLENGES